Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-08-07 Documents/M1/realizableFermionicM1/manuscript.tex
Additions to paper
Split section 3 in two: Moment Realizability... and Algebraic Moment Closures
Forgot to add algebraicClosures.tex.  Added appendix with some detail on the IMEX schemes discussed in the paper has been added (not complete)
Working on text discussing IMEX schemes.
More work on the imex section.
Minor adjustments to dg.tex and imex.tex.  Began work on updating DGIMEX.tex
Some work on Section 3 (removed proof of Lemma 1).  And other minor fixes
Added abstract

@@

\title{Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}}
\tnotetext[support]{This research is sponsored by ...}

@@

@@

\begin{abstract}
This paper ...
\end{abstract}

@@

\input{sections/intro}
\input{sections/model}
\input{sections/realizability}
\input{sections/dg}
\input{sections/imex}
\input{sections/DGIMEXscheme}
\input{sections/limiter}
\input{sections/numerical}
\input{sections/conclusion}
%\input{sections/appendix}
\clearpage

>>>>

\newcommand{\ee}[1]{{\color{red} #1}}
\newcommand{\rc}[1]{{\color{blue} #1}}

@@

\title{Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}}
\tnotetext[support]{
This research is sponsored, in part, by the Laboratory Directed Research and Development Program of Oak Ridge National Laboratory (ORNL), managed by UT-Battelle, LLC for the U. S. Department of Energy under Contract No. De-AC05-00OR22725.  
This research was supported by the Exascale Computing Project (17-SC-20-SC), a collaborative effort of the U.S. Department of Energy Office of Science and the National Nuclear Security Administration.  
Eirik Endeve was supported in part by NSF under Grant No. 1535130.}

@@

\author[ornl,utk-math]{Cory D. Hauck}
\ead{hauckc@ornl.gov}

@@

\address[utk-math]{Department of Mathematics, University of Tennessee Knoxville, TN 37996-1320}

\begin{abstract}
Building on the framework of Zhang \& Shu \cite{zhangShu_2010a,zhangShu_2010b}, we develop a realizability-preserving method to simulate transport of particles (fermions) through a background material using the two-moment model of radiation transport, which evolves angular moments of a phase space distribution function $f$.  
The two-moment model is closed using simple algebraic moment closures, e.g., as proposed by Cernohorsky \& Bludman \cite{cernohorskyBludman_1994} and Banach \& Larecki \cite{banachLarecki_2017a}.  
Variations of this model have recently been used to simulate neutrino transport in nuclear astrophysics applications --- including core-collapse supernovae and compact binary mergers.  
We employ the discontinuous Galerkin (DG) method for spatial discretization (in part to capture the asymptotic diffusion limit of the model) combined with implicit-explicit (IMEX) time integration to stably bypass short timescales induced by frequent interactions between particles and the background.  
Appropriate care is taken to ensure the method preserves strict algebraic bounds on the evolved moments (particle density and flux) as dictated by Pauli's exclusion principle, which demands a bounded distribution function (i.e., $f\in[0,1]$).  
This realizability-preserving scheme combines a suitable CFL condition, a realizability-preserving limiter, a closure procedure based on Fermi-Dirac statistics, and an IMEX scheme whose stages can be written as a convex combination of forward Euler steps combined with a backward Euler step.  
The IMEX scheme is formally only first-order accurate, but works well in the diffusion limit and reduces to the optimal second-order strong stability-preserving Runge-Kutta scheme of Shu \& Osher \cite{shuOsher_1988}.  
Numerical results demonstrate the realizability-preserving properties of the scheme.  
We also demonstrate that the use of algebraic moment closures not based on Fermi-Dirac statistics can lead to unphysical moments in the context of fermion transport.  
\end{abstract}

@@

\input{sections/intro}
\input{sections/model}
\input{sections/realizability}
\input{sections/algebraicClosures}
\input{sections/dg}
\input{sections/imex}
\input{sections/DGIMEXscheme}
\input{sections/limiter}
\input{sections/numerical}
\input{sections/conclusion}
\input{sections/appendix}

\clearpage
